Theories of deliberated choice

### 2024-05-13 simple.tex
Conjecture is now a theorem

>>>>

\begin{theorem}
  The two following statements are equivalent. 
  \begin{itemize}
    \item $\forall \hist: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$
    \item There exists no anonymous claim that holds and is falsifiable.
  \end{itemize}
\end{theorem}
\begin{proof}
  If the first one is false, then the claim $R({\allleadsto}(I))$ is not trivial, thus is falsifiable.

  If the first one holds, let us show that starting from $C^\text{HA}$ and integrating all relations that are not observably distinguishable, we obtain the trivial claim.

  Consider any observable whatsoever, $O \in \allpriobss$, and let us show that for some bijection $\sigma$ over $I$, $O \wsub ({\allleadsto} \circ \sigma)$.

  For each of the (finitely many) individuals that $O$ contains, we can find a different behavior $f_i$ that is in $\restr{{\allleadsto}(I)}{\intvl{\hist}}$, thus, with some $j_i \in I \suchthat {\allleadsto}(j_i) = f_i$, and that is compatible with what $O$ sees of $i$. We define $\sigma$ so that it maps each of those individuals $i$ to the individual $j_i$ with the corresponding behavior.
  The resulting relation ${\allleadsto} \circ \sigma$ is compatible with the observable.

  It follows that if the claim is not trivial, it is not falsifiable: pick any relation missing in the claim; it cannot be rejected by any observable.
\end{proof}
